Efficient pedigree recording for fast population genetics simulation

### 2018-01-14 forwards_paper.tex
para on known pedigress

>>>>

Another application of our methods would be the case of simulating coalescent histories conditional on known pedigrees.
The standard description of the Wright-Fisher coalescent averages over pedigrees.  However, conditional on a realized
pedigree, the distribution of coalescent times in the recent past differs from that of the unconditional coalescent
\citep{Wakeley2012-kw}.  For populations with known pedigrees \citep[\textit{e.g.}][]{Aguillon2017-ac}, it may be of use to
simulate transmission along such pedigrees for the purpose of inference.
